Interval Probability for Fuzzy Quantum Theories

### 2016-07-18 prob.tex
prob.tex \subsection{Interval-valued probability measures} finishing checking footnote...

As motivated above, an event $E_{1}$ may have an interval of probability
$[l_{1},r_{1}]$. Assume that another disjoint event $E_{2}$ has
interval probability $[l_{2},r_{2}]$, what is the interval probability
of the event $E_{1}\cup E_{2}$? The answer is somewhat subtle: although
it is possible to use the sum of the intervals $[l_{1}+l_{2},r_{1}+r_{2}]$
as the combined probability, one can do find a much tighter interval
if information \emph{against} the event (i.e., information about the
complement event) is also taken into consideration. Formally, for
a general event $E$ with probability $[l,r]$, the evidence that
contradicts $E$ is an evidence supporting the complement of $E$.
The complement of $E$ must therefore have probability $\left[1-r,1-l\right]$
which we abbreviate $1\tensor*[_{\mathscr{I}}]{-}{}\left[l,r\right]$,
where the preposing $\mathscr{I}$ specifies we subtracts intervals.
Given a collection of intervals $\mathscr{I}$, an $\mathscr{I}$\textendash interval-valued
probability measure is a function $\bar{\mu}:\events\rightarrow\mathscr{I}$
such that~\cite{JamisonLodwick2004}:\footnote{The lower and upper probability defined by Dempster~\cite{Dempster1967}
and the belief function defined by Shafer~\cite{Shafer1976} is a
special case of the interval-valued probability measures. } 
\begin{itemize}
\item $\bar{\mu}(\emptyset)=[0,0]$, 
\item $\bar{\mu}(\Omega)=[1,1]$, 
\item for any event $E$, $\bar{\mu}\left(\Omega\backslash
E\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(E\right)$, and 
\item for a collection $E_{i}$ of pairwise disjoint events, we have $\bar{\mu}\left(\bigcup_{i}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\bar{\mu}\left(E_{i}\right)$,
where $\tensor*[_{\mathscr{I}}]{\sum}{_{i}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i}}r_{i}\right]$.
We may drop the preposing $\mathscr{I}$ when summands are clearly intervals. 
\end{itemize}

>>>>

As motivated above, an event $E_{1}$ may have an interval of probability
$[l_{1},r_{1}]$. Assume that another disjoint event $E_{2}$ has
interval probability $[l_{2},r_{2}]$, what is the interval probability
of the event $E_{1}\cup E_{2}$? The answer is somewhat subtle: although
it is possible to use the sum of the intervals $[l_{1}+l_{2},r_{1}+r_{2}]$
as the combined probability, one can do find a much tighter interval
if information \emph{against} the event (i.e., information about the
complement event) is also taken into consideration. Formally, for
a general event $E$ with probability $[l,r]$, the evidence that
contradicts $E$ is an evidence supporting the complement of $E$.
The complement of $E$ must therefore have probability $\left[1-r,1-l\right]$
which we abbreviate $1\tensor*[_{\mathscr{I}}]{-}{}\left[l,r\right]$,
where the preposing $\mathscr{I}$ specifies we subtracts intervals.
Given a collection of intervals $\mathscr{I}$, an $\mathscr{I}$\textendash interval-valued
probability measure is a function $\bar{\mu}:\events\rightarrow\mathscr{I}$
such that~\cite{JamisonLodwick2004}:\footnote{The lower probability (belief) and the upper probability (plausibility)
defined by Dempster~\cite{Dempster1967} and Shafer~\cite{Shafer1976}
is a special case of the left-end and the right-end of the interval-valued
probability measure, and the right-end of the interval-valued probability
measure is a special case of capacity~\cite{Choquet1954,Graf1980,Goodman2013}.} 
\begin{itemize}
\item $\bar{\mu}(\emptyset)=[0,0]$, 
\item $\bar{\mu}(\Omega)=[1,1]$, 
\item for any event $E$, $\bar{\mu}\left(\Omega\backslash
E\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(E\right)$, and 
\item for a collection $E_{i}$ of pairwise disjoint events, we have $\bar{\mu}\left(\bigcup_{i}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\bar{\mu}\left(E_{i}\right)$,
where $\tensor*[_{\mathscr{I}}]{\sum}{_{i}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i}}r_{i}\right]$.
We may drop the preposing $\mathscr{I}$ when summands are clearly intervals. 
\end{itemize}
